*DCVtestkit*: an R package for analysis of quality control dilution curves

### 2022-10-14 Manuscript/manuscript.qmd
Modify the digits of percentages.

The workflow was tested on `r nrow(linear_dilution_summary)` simulated linear curves, `r nrow(lod_dilution_summary)` curves that plateau at low concentrations (labelled as LOD curves) and `r nrow(saturation_dilution_summary)` curves that plateau at high concentrations (labelled as Saturated curves)

```{r}
#| echo: false
#| label: tbl-simulation-result
#| tbl-cap-location: bottom
#| tbl-cap: "Simulation Results"
combined_dilution_summary |> 
  dplyr::select(c("curve_group", "wf2_group", 
                  "r_corr", "pra_linear")) |> 
  gtsummary::tbl_summary(
    by = "curve_group",
    statistic = list(
      wf2_group ~ "{n}/{N} ({p}%)"
    ) 
  ) |> 
  modify_header(all_stat_cols() ~ "**{level}**\nN = {n}") |> 
  gtsummary::modify_spanning_header(all_stat_cols() ~ "**Simulated Curve Types**") |>  
  gtsummary::as_flex_table() |> 
  flextable::set_table_properties(width = 1, layout = "autofit")

>>>>

Workflow $2$ was tested on `r nrow(linear_dilution_summary)` simulated linear curves, `r nrow(lod_dilution_summary)` curves that plateau at low concentrations (labelled as Limit of Detection curves) and `r nrow(saturation_dilution_summary)` curves that plateau at high concentrations (labelled as Saturated curves)

```{r}
#| echo: false
#| label: tbl-simulation-result
#| tbl-cap-location: bottom
#| tbl-cap: "Simulation Results"
combined_dilution_summary |> 
  dplyr::select(c("curve_group", "wf2_group", 
                  "r_corr", "pra_linear")) |> 
  gtsummary::tbl_summary(
    by = "curve_group",
    statistic = list(
      wf2_group ~ "{n}/{N} ({p}%)"
    ),
    digits = list(wf2_group ~ c(0, 0, 1),
                  r_corr ~ c(2),
                  pra_linear ~ c(0))
  ) |> 
  modify_header(all_stat_cols() ~ "**{level}**\nN = {n}") |> 
  gtsummary::modify_spanning_header(all_stat_cols() ~ "**Simulated Curve Type**") |>  
  gtsummary::as_flex_table() |> 
  flextable::set_table_properties(width = 1, layout = "autofit")
